---
title: 'AAEC 4484/ STAT(AAEC) 5484: Applied Economic Forecasting'
author: Your Name Here
date: |
    Homework #2 - Spring `r format(Sys.Date(),"%Y")` 
output: 
  pdf_document:
    keep_tex: no

header-includes:
 \usepackage{float} #fixes position of figures
geometry: margin=0.8in # sets the page margins

---

```{r setup, include=FALSE}
library(fpp3)
theme_set(theme_light()) # change if you would like.
knitr::opts_chunk$set(echo=TRUE, fig.pos = 'H', message=FALSE, warning = FALSE)
```


This assignment aims to enhance your understanding of time series and data patterns. It is intended to be straightforward.

**Instructions**: 

- **Where necessary, please ensure that your graphs and visuals have proper titles and axis labels.** 
- **Recall that you can use `help()` or `?seriesname` in your consoles to get general information on the dataset**. 

## Question 1: Basic Visualization of Time Series Data

i. Create time plots of the following time series: `Tobacco` from `aus_production`, `Lynx` from `pelt`, Intraday High prices (`High`) for `FB` from `gafa_stock`, `Demand` **for 2013** from `vic_elec`. 

- Please use the `grid.arrange()` function from the `gridExtra` package to arrange your plots as a `2 x 2` grid. 


ii. Briefly discuss any discernible pattern(s) you noticed in the data.

\newpage 

# Question 2: Assessing (Potential) Seasonality

In our earlier class sessions, we explored the idea of drawing a random sample of data. The exercise below offers a practical demonstration.

We will pull a random sample of the `aus_retail` data set by selecting a random `Series ID`, according to our chosen seed. 
**Set a seed of your choice to ensure you generate your draw of the data.**

```{r, eval=FALSE}
# Remove the eval = FALSE argument from the code chunk to run your codes.

set.seed(xxxx) #Set this to your preferred seed

```

i. Use the `autoplot()`, `gg_season()`, `gg_subseries()`, and `ACF() %>% autoplot()` functions to explore possible seasonality in your chosen sample.

- Please use the `grid.arrange()` function from the `gridExtra` package to arrange your plots. **You are free to organize them however you wish.**

- **It might be useful to change the `lag_max` (how about to 3 years of data?) in the ACF to ensure that you can see a fair bit of the pattern in the correlogram.** 


ii. What can you say about the series? Are there any seasonal patterns? Trends?


\newpage

# Question 3: White Noise

The `aus_livestock` series contains data on monthly "Meat production in Australia for human consumption". 

i. Using the `filter()` function, extract the number of **Cows and heifers** slaughtered in **Tasmania**. Store this variable as `cows`.

ii. Produce the `autoplot()` of `cows` and its correlogram. **Comment on any pattern noticed in both.** Does this series look like white noise? **Explain your answer.**


iii. Now, using the `difference()` and `mutate()` functions, create a new column, `diff`, that computes the **month-to-month** changes (`lag = 1`) in your `cows` series. Store this new data as `d.cows`. 
*I would suggest using the head() command on your differenced series in the console to ensure that the `diff` column looks as you would expect.*


iv. Produce an `autoplot()` of `diff` along with the associated correlogram.

    a. Does the first differenced data now look like white noise?
    b. Did differencing remove any potential seasonality in the data? 
    
**Recall that a simple yes/no will not suffice. You will need to explain your conclusion.**


v. Return to the `cows` series and again use the `difference()` and `mutate()` functions to create a new column called `diff12` that computes the **year-on-year** changes (`lag = 12`) in your `cows` series. Store this new data as `d12.cows`. 

*I would suggest using the `head(n = 14)` command on your `d12.cows` series in the console to ensure that the `diff12` column looks as you would expect.*


vi. Produce an `autoplot` of `diff12` along with the associated correlogram. 

     a. Does this new data, differenced at lag12, now look like white noise? **Recall that a simple yes will not suffice. You will need to explain your conclusion.**

    b. Did differencing remove all potential seasonality or trend in the data? If not, how would you solve this? **You are not required to do this. An intelligent answer based on the plots and your observations will suffice.**





