---
title: 'Applied Economic Forecasting'
author: "Homework Solution Sample Template"
output: pdf_document
header-includes:
 \usepackage{float} # Fixes position of graphs
 
geometry: margin=0.8in #sets the page margin as 0.8in all around
---

```{r setup, include=FALSE}
options(digits = 3) # Global argument to print values to 3dps
# I can use this chunk to 
 # - set the libraries necessary to execute the exercises below
 # - default options of my code chunks, graphs, etc.
library(fpp3)
theme_set(theme_light()) #set the default for all graphs in the pdf
knitr::opts_chunk$set(echo = TRUE, fig.pos = 'H') 
#produces codes and fixes the position of my graphs 
```

This template provides a guide of how I anticipate that your homework solutions will look. However, please feel free to exercise your creativity when producing your solutions. 

1. **Unless stated, please display the R chunk that produced your results.**

2. Please ensure you do a quick spell check of your document. Press **F7** on your keyboard.

3. An appropriate title must accompany all tables, graphs, and figures. Graph axes must be labeled where appropriate.

- **Whenever appropriate, please try to refer to the output.** Please take a look at the `.Rmd` file in this template to see how I am able to:

i. Add captions to my plots, 
ii. hyperlink and reference the plots automatically, and
iii. embed the results of variables computed and stored in the R chunks into my text. Gone are the days when you had to memorize the result and then type it over in your Word document. Once you have it stored as a variable, you can directly extract it in the document text.

# Question 1: Generating random variables

i. Generate a random normal variable, `x1`, that has 100 observations, a mean of 5, and a standard deviation of 5. That is $x1\sim N(5,5^2)$. 

- Use a seed of 01212023. 
- make `x1` a `tsibble` object (`x1.ts`). Assume that `x1.ts` represents *quarterly* values up to and including December 2021. **For simplicity, I first declared a `ts()` object and then used the `as_tibble()` function.**
- Using the `autoplot` function, plot `x1.ts`. 

```{r x1plots, fig.align="center", fig.height= 2, fig.cap= "Place caption for your plot here"} 

set.seed(01212023)
x1 <- rnorm(100, mean = 5, sd = 5)
x1.ts <- x1 %>% ts(end = c(2021,12), frequency = 4) %>% as_tsibble()
x1.ts %>% head() #Viewing the first 6 rows of the new data
x1.ts %>% autoplot(value, col = "green4") + 
  labs(title = "Plot of x1", x = NULL , y = NULL)
```
 
ii. Do you notice any discernible patterns (think trend, cycle, seasonality) in the plot?

**Answer: The observations of x1 in Figure \ref{fig:x1plots} appear to be random with no discernible pattern.**

iii. How do the sample mean and standard deviation compare to the population (actual) values?

```{r}
meanx1 <- mean(x1)
stdx1 <- sd(x1)
```

**Answer: The random draw of 100 observations has a mean of `r meanx1` and a standard deviation of `r  stdx1`. These are pretty close to their respective population values of 5 and 5, respectively.**

\newpage

# Question 2: White Noise

i. Plot the `ACF` of this series and comment on your observations.
```{r x1acf, fig.align="center", fig.cap= "ACF Plot of X1"} 
x1.ts %>% ACF(value, lag_max = 24) %>% 
  autoplot() + 
  labs(title = "ACF Plot of x1") 
```

**From the plots in Figure \ref{fig:x1acf}, all the autocorrelation statistics are within the 95% significance bands. Therefore, we can conclude that the series, `x1`,  is not distinguishable/different from a white noise process.**

